Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-05-11 tese2/16_implementation_content.tex
[RFT] rewriten model
[ADD] composite figure
[FIX] pseudo code for QR code content creation and implementation, fix non return to real time

\begin{minipage}[!htb]{\linewidth}
\begin{lstlisting}[caption={Pseudo code for QR code leaving detection},label={lst:pseudo_qrcode},language=JavaScript]
var ongoingCodesMap = {};
function onCodeFound(content) {
	var startingTime = getCurrentTime() - getUserOffset();
	var hash = md5(content);
	if(ongoingCodesMap[hash] == null){
		sendQRCodeToEditingUser(hash,content);
	}
	ongoingCodesMap[hash] = startingTime;
	waitTwoSeconds(); // onCodeFound() may be called from other threads
	var newestTime = ongoingCodesMap[hash]; 
	if(newestTime == startingTime){
		var endingTime = getCurrentTime() - getUserOffset();
		ongoingCodesMap[hash] = null; 
		sendQRCodeToEditingUser(hash,null); // remove from UI
		insertContentIntoDatabase(startingTime,endingTime,content);
		sendContentToUsers(startingTime,endingTime,content);
	}
}
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}[!htb]{\linewidth}
\begin{lstlisting}[caption={Pseudo code for hyper content scheduler},label={lst:pseudo_render},language=JavaScript]
function scheduleContent() {
    var navigatedTime = getCurrentTime() - getUserOffset();
    while ( hasLocalEvents() ) {
        if ( firstEventIsOlderThanNavigatedTime() ) {
            if ( firstEventIsStart() ) {
            	addHtmlLayer(event);
            } else {
            	removeHtmlLayer(event);
            }
            removeFirstEvent();
        } else {
            break;
        }
    }
    if ( hasNoLocalEvents() ) {
    	return;	// nothing to do
    } 
    if ( hasNoStartEvents() && serverHasMoreContent() ) { 
       	requestContentFromServer(navigatedTime);
    } else {
        waitUntilNextEvent();
        scheduleContent();
    }
}
\end{lstlisting}
\end{minipage}

@@

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=\textwidth]{figures/timeline.png}
		\caption{Interactive time-line}
		\label{fig:timeline}
	\end{figure}

@@

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.7\textwidth]{figures/annotation.png}
		\caption{Creating a time annotation}
		\label{fig:annotation}
	\end{figure}

@@

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.8\textwidth]{figures/timelink.png}
		\caption{Time link creation}
		\label{fig:timelink}
	\end{figure}

@@

\begin{figure}[!htb]
\centering
\begin{minipage}[b]{0.55\linewidth}
\centering

		\includegraphics[width=\textwidth]{figures/search.png}
	      a) Result list
\label{fig:minipage1}
\end{minipage}
\quad
\begin{minipage}[b]{0.40\linewidth}
		\centering

		\includegraphics[width=\textwidth]{figures/search2.png}
	       b) Selected result
\label{fig:minipage2}
\end{minipage}

		\caption{Example of search results}
		\label{fig:search}
\end{figure}

@@

@@

@@

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.8\textwidth]{figures/devices.png}
		\caption{Multiple devices per user}
		\label{fig:devices}
	\end{figure}

>>>>

\begin{minipage}[!htb]{\linewidth}
\begin{lstlisting}[caption={Pseudo code for QR code leaving detection},label={lst:pseudo_qrcode},language=JavaScript]
var ongoingCodesMap = {};
var startedCodesMap = {}

function onCodeFound(content) {
	var startingTime = getCurrentTime() - getUserOffset();
	var hash = md5(content);

	if(startedCodesMap[hash] == null) {
		sendQRCodeToEditingUser(hash,content);
		startedCodesMap[hash] = currentTime;
	}

	ongoingCodesMap[hash] = currentTime;
	waitTwoSeconds(); // onCodeFound() may be called from other threads
	var newestTime = ongoingCodesMap[hash]; 
	if(newestTime == currentTime){
		var startingTime = startedCodesMap[hash];
		var endingTime = getCurrentTime() - getUserOffset();

		startedCodesMap[hash] = null; 
		ongoingCodesMap[hash] = null;

		sendQRCodeToEditingUser(hash,null); // remove from UI
		insertContentIntoDatabase(startingTime,endingTime,content);
		sendContentToUsers(startingTime,endingTime,content);
	}
}
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}[!htb]{\linewidth}
\begin{lstlisting}[caption={Pseudo code for hyper content scheduler},label={lst:pseudo_render},language=JavaScript]
function scheduleContent() {
    var navigatedTime = getCurrentTime() - getUserOffset();
    while ( hasLocalEvents() ) {
        if ( firstEventIsOlderThan(navigatedTime)) {
            if ( firstEventIsStart() ) {
            	addHtmlLayer(event);
            } else {
            	removeHtmlLayer(event);
            }
            removeFirstEvent();
        } else {
            break;
        }
    }
    if ( hasNoLocalEvents() && !serverHasMoreContent()) {
    	return;	// nothing to do
    } 
    if ( hasNoStartEvents() && serverHasMoreContent() ) { 
       	requestContentFromServer(navigatedTime);
    } else {
        waitUntilNextEvent();
        scheduleContent();
    }
}
\end{lstlisting}
\end{minipage}

@@

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.8\textwidth]{figures/timeline.png}
		\caption{Interactive time-line}
		\label{fig:timeline}
	\end{figure}

@@

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.5\textwidth]{figures/annotation.png}
		\caption{Creating a time annotation}
		\label{fig:annotation}
	\end{figure}

@@

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.6\textwidth]{figures/timelink.png}
		\caption{Time link creation}
		\label{fig:timelink}
	\end{figure}

@@

\begin{figure}[!htb]
	\centering
	\begin{minipage}[b]{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{figures/search.png}
		a) Result list
	\end{minipage}
	\quad
	\begin{minipage}[b]{0.30\linewidth}
		\centering
		\includegraphics[width=\textwidth]{figures/search2.png}
	    b) Selected result
	\end{minipage}
	\caption{Example of search results}
	\label{fig:search}
\end{figure}

@@

		The composite operation, as shown on figure \ref{fig:wcomposite} works by decoding the incoming client streams, mixing audio and video and encoding again to send back to users.

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.6\textwidth]{figures/wcomposite.pdf}
		\caption{Stream decoding, composition and encoding}
		\label{fig:wcomposite}
	\end{figure}

@@

	\begin{figure}[!htb]
		\centering
		\includegraphics[width=0.6\textwidth]{figures/devices.png}
		\caption{Multiple devices per user}
		\label{fig:devices}
	\end{figure}

@@
